Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-11-27 paper/sheaf_lics.tex
[wording] improve wording in concessive statement

Also proposition truncation could be seen as a primitive type former
in homotopy type theory, it can be defined using higher inductive
types~\cite{lumsdaine2011higher,lumsdaine2013higher}. We adopt this
point of view as it allows one to maintain the slogan that homotopy type
theory is type theory plus univalence and higher inductive types.
%

>>>>

Although proposition truncation could be seen as a primitive type former
in homotopy type theory, it can also be defined using higher inductive
types~\cite{lumsdaine2011higher,lumsdaine2013higher}. We adopt this
point of view as it allows one to maintain the slogan that homotopy type
theory is type theory plus univalence and higher inductive types.
%
